Assignment 3

### 2015-02-16 rmtw/a3/latex8.tex
Minor changes to 2nd section

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Company X tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the result gathered from analyzing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for that is that the goal of our study is to analyze MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in CITE XXX. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies CITE XXX.

In the initial stage of the study, careful planning was conducted. The two major goals of this phase were to a) find meaningful objectives and design for the research, and b) facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning related to communication with Company X, to facilitate the interviews. A timeline for the interviews was created and established with Company X. The objective of analysing change implementation in enviroments which are split into by two different development activities was also defined during this stage.

\SubSection{Preparation for Data Collection}
During this stage the interviews were designed. The initial design of the interview was pilot tested on three employees of Company X. The results from the pilot tests were used to test if the interviews would fulfil the objective of the study. The number of subjects for the main interviews were 15. They were sampled randomly from employment records in Company X.

During this stage, the all ethical precautions of the study were taken. It was established that Company X wanted to remain anonymous and that all interviews must happen on voluntary basis. An agreement on to which extent Company X's documentation could be used was also made during this stage.

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX. The subjects of the interviews can be divided into three sub-groups: a) Managers b) Developers c) Change Agents. Data triangulation has been used to compare and verify the results based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes. The interviews have been carried out using a mix of open-ended and close-ended questions, and a semi-structured approach has been used. The fact that the interviewees have widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to get results that are closely related to eachother, so that meaningful comparison and analysis can be carried out. Company X's change process documentation has also been analysed to provide further depth to the analysis. Please see Appendix A for a full list of interview questions.

\SubSection{Data Analysis}
The data analysis of the interviews has been done in tandem with the data gathering to be able to iteratively improve the data collection process. This data analysis has had the main purpose of generating hypotheses and to refine the research questions. The interviews were analysed by manually reading and comparing answers. Spreadsheets and tables were also used to provide an overview of the results.

When all the interview data had been collected, the data analysis goal was switched to focus on confirmation of the hypothesis. As mentioned in Section IV. C, data triangulation was the main tool used to confirm the hypothesis.

>>>>

\SubSection{Case Study Design}
The study has been conducted with an exploratory goal in mind. Analysing how Company X tackle the problems related to the research questions has been the most central part of the study. Because of the exploratory nature of the study, a flexible process design has been used. The study has been carried out using an iterative approach, where the data collected, and the results gathered from analysing the data has been the main driver for shaping and improving the scope and goal of the study. The research has been conducted using a case study approach. The reason for this is that the goal of our study is to analyse MDSD, which is a common practice in software engineering, in a very specific setting. This line of thought is supported by Runesson \& Höst in CITE XXX. Runesson \& Höst also outline that a case study approach is well-suited for exploratory studies CITE XXX.

During the initial stage of the study, careful planning was conducted. The two major goals of this phase were to find meaningful objectives with an appropriate design for the research and secondly to facilitate and design the interviews. Although a flexible approach was taken, major effort was spent on planning the study. Most of the planning was related to communicating with Company X to facilitate the interviews. A time-line for the interviews was created and established with company X. The objective of analysing change implementation in environments which are split into by two different development activities was also defined during this stage.

\SubSection{Preparation for Data Collection}
During this stage the interviews were designed. The initial design of the interview was pilot tested on three employees of Company X. The results from the pilot tests were used to test if the interviews would fulfil the objective of the study. The number of subjects for the main interviews was 15. They were sampled randomly from employment records at Company X.

During this stage, all ethical precautions of the study were taken. It was established that Company X wanted to remain anonymous and that all interviews must happen on a voluntary basis. An agreement on to what extent Company X's documentation could be used was also made during this stage.
%Add what was agreed

\SubSection{Data Gathering}
The data has mainly been gathered through first degree interviews CITE LETHBRIDGE 2005 XXX. The subjects of the interviews were divided into three sub-groups; Managers, Developers and Change Agents. Data triangulation was performed to compare and verify the results based on which role the interviewee had. The reason this was done was to reduce risk of, for example, change agents having a positive bias towards previously implemented changes. The interviews were carried out using a mix of open-ended and close-ended questions in combination with a semi-structured approach. The fact that the interviewees had widely differing backgrounds and roles was the main reason for not using a structured approach. A semi-structured approach was chosen over a unstructured approach to be able to obtain results which were closely related to each other. This was performed so that meaningful comparison and analysis could be carried out. Company X's change process documentation was also analysed to provide further depth to the analysis already performed. Please see Appendix A for a full list of interview questions.

\SubSection{Data Analysis}
The data analysis of the interviews were completed in tandem with the data gathering phase. This was performed so that we could iteratively improve upon the data collection process. The main purpose of analysing this data was to generate hypotheses and to refine the proposed research questions. The interviews were analysed by manually reading and comparing answers between the respondents. Spreadsheets and tables were used to provide an overview of the results.

Once all the interview data had been collected, the goal of the data analysis shifted to focus upon confirmation of the hypothesis. As mentioned in Section IV. C, data triangulation was the primary tool used to confirm the hypothesis.
